A comparison of design-based and model-based approaches for finite population spatial data.

### 2021-10-22 inst/manuscript/manuscript.Rmd
added to vignett and got rid of effective range line.

We used a crossed design with the simulation parameters given in Table \ref{tab:parmtab} for a total of 36 scenarios. All scenarios used exponential correlation with a  $\sqrt{2} / 3$ for $N = 900$ response values simulated on the unit square in either random locations (Layout = Random) or gridded locations (Layout = Gridded). The range was chosen so that the decayed to nearly zero at the largest distance possible in the domain, $\sqrt{2}$, otherwise known as the "effective" range (for the exponential covariance, the effective range is $3\phi$). The mean for the spatial process generating the response was set to zero.

>>>>

We used a crossed design with the simulation parameters given in Table \ref{tab:parmtab} for a total of 36 scenarios. All scenarios used exponential correlation with a  $\sqrt{4} / 3$ for $N = 900$ response values simulated on the unit square in either random locations (Layout = Random) or gridded locations (Layout = Gridded). The mean for the spatial process generating the response was set to zero.

<!-- The range was chosen so that the decayed to nearly zero at the largest distance possible in the domain, $\sqrt{2}$, otherwise known as the "effective" range (for the exponential covariance, the effective range is $3\phi$). -->
